### 2024-10-21 paper/paper.qmd
Initial Draft - simulate data
Create - simulated_data.csv
Upload - 00-simulate_data.R
Upload - paper.qmd

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

Discussion of the survey’s methodology (North York)

Sample: a topline sample size of at least 100

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-10-21 scripts/00-simulate_data.R

@@ -11,42 +11,57 @@
 
 #### Workspace setup ####
 library(tidyverse)
-set.seed(853)
+df <- read_csv("../data/01-raw_data/president_polls.csv")
 
+max_id <- max(df$poll_id)
+
+pollster <- unique(df$pollster)
+
+pollscore <- unique(df$pollscore)
+
+party <- unique(df$party)
+
+max_size <- max(df$sample_size, na.rm = TRUE)
+
+answer <- unique(df$answer)
+percentages <- prop.table(table(df$answer)) * 100 #percentages for each answer
+precentages <- as.numeric(percentages[match(answer, names(percentages))])  # Align with `answer`
 
 #### Simulate data ####
-# State names
-states <- c(
-  "New South Wales",
-  "Victoria",
-  "Queensland",
-  "South Australia",
-  "Western Australia",
-  "Tasmania",
-  "Northern Territory",
-  "Australian Capital Territory"
-)
+sim_size <- 2000
 
-# Political parties
-parties <- c("Labor", "Liberal", "Greens", "National", "Other")
+# Poll IDs
+sim_id <- sample(1:max_id, sim_size, replace = TRUE)
+
+# Pollster
+sim_pollster <- sample(pollster, sim_size, replace = TRUE)
+
+# PollScore
+sim_pollscore <- sample(pollscore, sim_size, replace = TRUE)
+
+# Party
+sim_party <- sample(party, sim_size, replace = TRUE)
+
+# Sample Size
+sim_sample_size <- sample(1:max_size, sim_size, replace = TRUE)
+
+# Percentage
+sim_pct <- pct <- rpois(2000, 50)
+
+# Answer
+sim_answer <- sample(answer, sim_size, replace = TRUE, prob = precentages)
 
 # Create a dataset by randomly assigning states and parties to divisions
-analysis_data <- tibble(
-  division = paste("Division", 1:151),  # Add "Division" to make it a character
-  state = sample(
-    states,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.25, 0.25, 0.15, 0.1, 0.1, 0.1, 0.025, 0.025) # Rough state population distribution
-  ),
-  party = sample(
-    parties,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.40, 0.40, 0.05, 0.1, 0.05) # Rough party distribution
-  )
-)
 
+sim_data <- tibble(
+  Poll_ID = sim_id,
[…]

### 2024-10-21 paper/paper.qmd
update paper.qmd

@@
 ---
-title: "My title"
+title: "2024 US Presidential Election Forecast Model"
 subtitle: "My subtitle if needed"
 author: 
-  - First author
-  - Another author
+  - Viet Nguyen
+  - Yihang Xu
+  - Doran Wang
 thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
@@
 library(tidyverse)
-library(palmerpenguins)
+library(readr)
+library(dplyr)
+library(knitr)
+
+clean_data <- read.csv("/Users/nguyenviet/Documents/term-paper-2/data/01-raw_data/clean_data.csv")
+
 ```
@@
 
-Overview paragraph
+The 2024 U.S.
+Presidential Election Forecast Model aims to provide a comprehensive analysis of polling data to predict potential outcomes in the upcoming election.
+Utilizing a robust dataset that includes over 50 variables, such as pollster ratings, sample sizes, election dates, candidate affiliations, and polling methodologies, this model seeks to offer a nuanced understanding of voter preferences and trends across the country.
 
-Estimand paragraph
-
-Results paragraph
-
-Why it matters paragraph
-
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+Key factors, such as pollster transparency scores, polling population characteristics, and election stages, are incorporated to ensure accuracy and relevance.
+By leveraging this data, the model can account for regional dynamics, partisan leanings, and shifts in voter sentiment, providing detailed insights into the evolving electoral landscape.
+This forecast model represents a data-driven approach to understanding the political climate as candidates navigate the road to the presidency.
 
 # Data {#sec-data}
-
-## Overview
-
-We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...
-
-Overview text
-
-## Measurement
-
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
-
-## Outcome variables
-
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
-
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
 
@@
 #| echo: false
+#| warning: false
+#| message: false
 
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
+ggplot(clean_data, aes(x = answer)) +
+  geom_bar(fill = "red", color = "black") +
+  labs(title = "Distribution of Answers", x = "Answer", y = "Count") +
+  theme_minimal()
 ```
-
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
 
@@
 
-analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
+ggplot(clean_data, aes(x = answer, y = pct, fill = party)) +
+  geom_bar(stat = "identity", color = "black") +
+  labs(title = "Percentage of Support for Each Candidate", x = "Candidate", y = "Percentage") +
   theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
+  scale_y_continuous(labels = scales::percent_format(scale = 1)) + # Converts y-axis to percentage format
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotates x-axis labels
 ```
-
-Talk way more about it.
-
-## Predictor variables
-
-Add graphs, tables and text.
-
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
 
@@
 
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+In the 2024 U.S.
+Presidential Election Forecast Model, the percentage of voter support for a candidate, represented by the variable pct, is modeled as the response variable.
+The predictors in this model include the candidate's political affiliation (party), the size of the sample surveyed (sample_size), the rating of the pollster based on their historical accuracy (numeric_grade), and the geographic location of the poll, represented by the variable state.
+By incorporating these predictors, the model aims to account for both the qualitative and quantitative factors that influence polling outcomes.
+The party variable captures the effect of political affiliation on voter support, while sample_size adjusts for the variability in poll precision.
+Numeric_grade reflects the reliability of the pollster, and state introduces regional variations in voting preferences.
+This model structure enables a detailed analysis of the factors driving election polling percentages across different states and political contexts.
 
 ## Model set-up
-
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
-
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+$$
+\text{pct} = \beta_0 + \beta_1 \cdot \text{pollscore} + \beta_2 \cdot \text{sample size} + \beta_3 \cdot \text{numeric grade} + \epsilon
+$$
+where $\beta_0$ is the intercept, $\beta_1$, $\beta_2$, $\beta_3$, $\beta_4$ are the coefficients associated with the predictors, and $\epsilon$ represents the error term.
+This model accounts for both qualitative variables, like the party and state, as well as quantitative variables, such as sample size and pollster rating.
 
 ### Model justification
-
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+model <- lm(pct ~ pollscore + sample_size + numeric_grade, data = raw_data)
+summary(model)
+```
 
@@
 
-Our results are summarized in @tbl-modelresults.
-
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-
-library(rstanarm)
-
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
-```
-
 # Discussion
-
-## First discussion point {#sec-first-point}
-
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
-
-## Second discussion point
-
-Please don't use these as sub-heading labels - change them to be what your point actually is.
-
-## Third discussion point
-
-## Weaknesses and next steps
-
-Weaknesses and next steps should also be included.
-
-\newpage
-
-\appendix
 
@@
 
-Discussion of the survey’s methodology (North York)
-
-Sample: a topline sample size of at least 100
-
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
-```
-
-## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
-```
-
-\newpage
-
 # References

### 2024-10-22 paper/paper.qmd
update paper.qmd

@@
 #| message: false
-model <- lm(pct ~ pollscore + sample_size + numeric_grade, data = raw_data)
+model <- lm(pct ~ pollscore + sample_size + numeric_grade, data = clean_data)
 summary(model)

### 2024-10-22 scripts/02-download_data.R
update download_data

@@ -1,26 +1,27 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Downloads and saves the data from FiveThrityEight
+# Author: Viet Nguyen
+# Date: 21 October 2024
+# Contact: viethoang.nguyen@utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: NA
+# Any other information needed? NA
 
 
 #### Workspace setup ####
-library(opendatatoronto)
 library(tidyverse)
-# [...UPDATE THIS...]
+library(readr)
+library(dplyr)
 
 #### Download data ####
-# [...ADD CODE HERE TO DOWNLOAD...]
+raw_data <- read_csv("/Users/nguyenviet/Documents/term-paper-2/data/01-raw_data/president_polls.csv")
 
-
+clean_data <- raw_data |> select(pollster, display_name, 
+                                 pollster_rating_id, numeric_grade, pollscore,
+                                 transparency_score, state, start_date, end_date, 
+                                 sample_size, election_date, 
+                                 party, answer, candidate_name, pct) %>%
+  filter(pollster=="Siena/NYT") %>% filter(!is.na(state))
 
 #### Save data ####
-# [...UPDATE THIS...]
-# change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(the_raw_data, "inputs/data/raw_data.csv") 
-
-         
+write_csv(clean_data, "/Users/nguyenviet/Documents/term-paper-2/data/01-raw_data/clean_data.csv")

### 2024-11-02 scripts/03-clean_data.R
Upload by Doran Wang
-Change the 'Rproj' name
-Update the '02-download_data.R' and '03-clean_data.R'
-Upload the NYT_data.csv in 'data' file
-Upload the example.R in 'models' file

@@ -1,44 +1,24 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans the president polls data to the Siena/NYT pollster only data [...UPDATE THIS...]
+# Author: 
+# Date:
+# Contact: 
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Access to the president_polls.csv first
 
 #### Workspace setup ####
 library(tidyverse)
 
 #### Clean data ####
-raw_data <- read_csv("inputs/data/plane_data.csv")
+raw_data <- read_csv("data/01-raw_data/president_polls.csv")
 
-cleaned_data <-
+NYT_data <-
   raw_data |>
   janitor::clean_names() |>
-  select(wing_width_mm, wing_length_mm, flying_time_sec_first_timer) |>
-  filter(wing_width_mm != "caw") |>
-  mutate(
-    flying_time_sec_first_timer = if_else(flying_time_sec_first_timer == "1,35",
-                                   "1.35",
-                                   flying_time_sec_first_timer)
-  ) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "490",
-                                 "49",
-                                 wing_width_mm)) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "6",
-                                 "60",
-                                 wing_width_mm)) |>
-  mutate(
-    wing_width_mm = as.numeric(wing_width_mm),
-    wing_length_mm = as.numeric(wing_length_mm),
-    flying_time_sec_first_timer = as.numeric(flying_time_sec_first_timer)
-  ) |>
-  rename(flying_time = flying_time_sec_first_timer,
-         width = wing_width_mm,
-         length = wing_length_mm
-         ) |> 
+  select(pollster,methodology,population,population_full,sample_size,numeric_grade,pollscore) |>
+  filter(pollster == "Siena/NYT") |>
   tidyr::drop_na()
 
 #### Save data ####
-write_csv(cleaned_data, "outputs/data/analysis_data.csv")
+write_csv(NYT_data, "data/02-analysis_data/NYT_data.csv")
+

### 2024-11-02 paper/paper.qmd

@@
 format: pdf
+toc: true
+toc-title: "Table of Contents"
 number-sections: true
@@
 
-clean_data <- read.csv("/Users/nguyenviet/Documents/term-paper-2/data/01-raw_data/clean_data.csv")
-
+clean_data <- read_csv("../data/01-raw_data/clean_data.csv")
+nyt_data <- read_csv("../data/02-analysis_data/NYT_data.csv")
 ```
@@
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
+#| echo: false
+#| eval: true
+#| label: tbl-cleaned_data
+#| tbl-cap: "Sample Cleaned Data"
+#| warning: false
+
+clean_data |>
+  head(5) |>
+  kable(col.names = c("Pollster","Display Name","Pollster Rating ID","Grade","Poll Score", "Transparency Score","State","Start Date","End_Date", "Sample Size", "Election Date", "Party", "Answer","Candidate Name","Percentage"),
+    booktabs = TRUE
+  )
+
+```
+
+```{r}
+#| label: fig-distribution_Answers
+#| fig-cap: Distribution of Answers
 #| echo: false
@@
 ```{r}
-#| label: fig-planes
+#| label: fig-histrpct
 #| fig-cap: Relationship between wing length and width
@@
 
+# Discussion of the survey’s methodology of Siena/NYT
+
+## Population, Frame, and Sample
+
+-Population:
+
+-Frame:
+
+-Sample:
+a topline sample size of at least 100
+
+## Sample Recruitment Method
+
+## Sampling Approach's trade-offs
+
+-Strengths:
+
+-Weaknesses:
+
+## How is non-response handled
+
+## What is good and bad about the questionnaire
+
+### Advantages
+
+### Disadvantages
+
+\newpage
+
 # References

### 2024-11-02 paper/paper.qmd

@@
   - Doran Wang
-thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
+thanks: "Code and data are available at: [https://github.com/vietng04/2024-US-Presidential-Election-Forecast](https://github.com/vietng04/2024-US-Presidential-Election-Forecast)."
 date: today
 date-format: long 
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This paper uses aggregate polling data and 'STH' modeling methods to predict the 2024 U.S.
+presidential election outcome.
+The Model use the factors related to the polls on Donald Trump’s support rate.
+The study also includes a deep-dive analysis of methodology on selected pollster, the New York Times (NYT), and then an idealized methodology and survey for predicting elections on a limited budget."
 format: pdf
@@
 # Data {#sec-data}
+The data used in this paper came from the FiveThirtyEight [@fivethirtyeight2024].
+Data were cleaned and analyzed using the open source statistical programming language R [@citeR].
+Libraries `tidyverse` [@citeTidyverse], `janitor` [@Citejan], `knitr` [@citeknitr], and `dplyr` [@citedplyr] were used for simulating, cleaning and testing.
+Graphics were made using `ggplot2` [@citeGG].
+
+## Sample Data
 
@@
 clean_data |>
+  select(1:5) |>      # Select the first 3 columns
   head(5) |>
-  kable(col.names = c("Pollster","Display Name","Pollster Rating ID","Grade","Poll Score", "Transparency Score","State","Start Date","End_Date", "Sample Size", "Election Date", "Party", "Answer","Candidate Name","Percentage"),
+  kable(
+    col.names = names(clean_data)[1:5],  # Automatically get the first 3 column names to match data
     booktabs = TRUE
   )
-
 ```
@@
   geom_bar(fill = "red", color = "black") +
-  labs(title = "Distribution of Answers", x = "Answer", y = "Count") +
+  labs(x = "Answer", y = "Count") +
   theme_minimal()
@@
 ```{r}
-#| label: fig-histrpct
-#| fig-cap: Relationship between wing length and width
+#| label: fig-histogram_pct
+#| fig-cap: Percentage of Support for Each Candidate
 #| echo: false
@@
   geom_bar(stat = "identity", color = "black") +
-  labs(title = "Percentage of Support for Each Candidate", x = "Candidate", y = "Percentage") +
+  labs( x = "Candidate", y = "Percentage") +
   theme_minimal() +
@@
 
+\newpage
+
+\appendix
+
 # Appendix {-}

### 2024-11-02 paper/paper.qmd
update paper.qmd

@@
 clean_data <- read_csv("../data/01-raw_data/clean_data.csv")
+raw_data <- read_csv("../data/01-raw_data/president_polls.csv")
 nyt_data <- read_csv("../data/02-analysis_data/NYT_data.csv")
@@
 $$
-\text{pct} = \beta_0 + \beta_1 \cdot \text{pollscore} + \beta_2 \cdot \text{sample size} + \beta_3 \cdot \text{numeric grade} + \epsilon
+\text{pct} = \beta_0 + \beta_1 \cdot \text{pollscore} + \beta_2 \cdot \text{sample size} + \beta_3 \cdot \text{numeric grade} + \beta_4 \cdot \text{transparency score} + \epsilon
 $$
@@
 #| message: false
-model <- lm(pct ~ pollscore + sample_size + numeric_grade, data = clean_data)
-summary(model)
+trump_data <- raw_data %>% filter(candidate_name == "Donald Trump")
+trump_model <- lm(pct ~ pollscore + sample_size + numeric_grade + transparency_score, data = trump_data)
+summary(trump_model)
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+harris_data <- raw_data %>% filter(candidate_name == "Kamala Harris")
+harris_model <- lm(pct ~ pollscore + sample_size + numeric_grade + transparency_score, data = harris_data)
+summary(harris_model)
 ```
@@
 # Results
+## Trump
+The model estimates the influence of several predictors on the dependent variable.
+The intercept is estimated at 48.56, indicating the baseline level of the dependent variable when all predictors are held at zero.
+
+Poll Score: The coefficient for the poll score is -2.232, which is statistically significant (p < 0.001).
+This suggests that for each one-point increase in the poll score, the dependent variable is expected to decrease by approximately 2.232 units, holding all other factors constant.
+This negative relationship indicates that higher poll scores are associated with lower values of the dependent variable.
+
+Sample Size: The coefficient for sample size is -0.0002085, also significant (p < 0.001).
+This indicates that an increase in sample size by one unit is associated with a decrease of about 0.0002085 units in the dependent variable.
+Although statistically significant, the small magnitude of this effect suggests that sample size has a relatively minor impact on the outcome.
+
+Numeric Grade: The numeric grade coefficient is -1.814, which is significant at the p < 0.001 level.
+This means that for every one-point increase in the numeric grade, the dependent variable decreases by about 1.814 units, again holding other factors constant.
+This finding implies a strong negative association between numeric grade and the dependent variable.
+
+Transparency Score: The transparency score has a coefficient of -0.0676, which is not statistically significant (p = 0.135).
+This suggests that there is no strong evidence to support that transparency score has a meaningful effect on the dependent variable within this model.
+
+## Harris
+The model investigates the impact of several predictors on the dependent variable, with the following key findings:
+
+Intercept: The intercept is estimated at 42.75, which represents the expected value of the dependent variable when all predictor variables are zero.
+
+Poll Score: The coefficient for the poll score is 1.629, with a p-value of 4.44e-05, indicating statistical significance at the p < 0.001 level.
+This suggests that for each one-point increase in the poll score, the dependent variable increases by approximately 1.629 units, holding all other variables constant.
+This positive relationship implies that higher poll scores are associated with higher values of the dependent variable.
+
+Sample Size: The coefficient for sample size is 0.0001457, which is also statistically significant (p = 0.00114).
+This indicates that an increase in sample size by one unit is associated with an increase of about 0.0001457 units in the dependent variable.
+Although significant, this effect size is relatively small.
+
+Numeric Grade: The numeric grade coefficient is 3.448, with a p-value of 2.35e-11, which is highly significant.
+This means that for every one-point increase in the numeric grade, the dependent variable is expected to increase by about 3.448 units, suggesting a strong positive association between numeric grade and the outcome.
+
+Transparency Score: The coefficient for the transparency score is -0.4207, and it is statistically significant (p = 6.70e-11).
+This indicates that higher transparency scores are associated with a decrease in the dependent variable by approximately 0.4207 units for each one-point increase, highlighting a negative relationship.
 
 # Discussion
+The analysis of the two models, one for Trump and the other for Harris, reveals distinct patterns in their predictor relationships and overall model performance, providing insights into their potential electoral outcomes.
 
-\newpage
+Model Comparisons
+Significance of Predictors:
 
-\appendix
+Trump’s Model: Key predictors such as poll score, sample size, and numeric grade all exhibit significant negative relationships with the dependent variable.
+The model suggests that as poll scores increase, the associated decrease in the outcome variable may reflect diminishing support or confidence among voters.
+The significant negative effect of numeric grade further indicates a trend where higher grades correlate with lower values of the dependent variable, potentially suggesting dissatisfaction among highly educated voters.
+Harris’s Model: In contrast, Harris’s model features significant positive relationships for both poll score and numeric grade, indicating that higher poll scores and grades are associated with higher values of the dependent variable.
+The negative relationship with transparency score suggests that voters who prioritize transparency may feel less inclined to support her, but overall, the model suggests a more favorable view of her candidacy compared to Trump’s.
+Model Fit:
+
+Trump’s model has a multiple R-squared of 0.03238, suggesting that only 3.24% of the variability in the dependent variable is explained.
+In comparison, Harris’s model has a higher multiple R-squared of 0.06257, indicating that about 6.26% of the variance is explained by her predictors.
+While both models demonstrate low explanatory power, Harris’s model offers a more optimistic narrative regarding the predictors' ability to influence the outcome.
+Magnitude of Effects:
+
+The coefficients in Harris’s model indicate more substantial effects of the predictors, particularly with numeric grade having a significant positive impact (3.448) compared to Trump’s negative impact (-1.814).
+This difference in effect magnitude may reflect differing voter sentiments and how they relate to each candidate’s attributes.
+Statistical Significance:
+
+Both models reveal highly significant p-values for several predictors, indicating that the relationships identified are statistically robust.
+However, the overall model significance is more pronounced in Harris’s model, particularly in light of the lower R-squared values for both models.
+Likely Outcome
+Considering the predictors and their implications for voter sentiment, Harris appears to have the upper hand in this analysis.
+The positive associations with poll scores and numeric grades in her model suggest a stronger alignment with voter preferences.
+Additionally, the higher R-squared value and overall model fit imply that her candidacy resonates more favorably with the electorate.
+
+Moreover, the contrast in the effect of the transparency score could indicate differing voter priorities.
+Harris’s potential appeal to voters valuing transparency may be a double-edged sword, yet it underscores a critical difference in how the two candidates are perceived regarding their public image.
 
@@
 
-# Discussion of the survey’s methodology of Siena/NYT
-
-## Population, Frame, and Sample
-
--Population:
-
--Frame:
-
--Sample:
-a topline sample size of at least 100
-
-## Sample Recruitment Method
-
-## Sampling Approach's trade-offs
-
--Strengths:
-
--Weaknesses:
-
-## How is non-response handled
-
-## What is good and bad about the questionnaire
-
-### Advantages
-
-### Disadvantages
-
-\newpage
-
 # References

### 2024-11-02 scripts/05-exploratory_data_analysis.R
update EDA

@@ -1,37 +1,37 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Model the data to understand the data better before applying any predictive models or deeper analysis
+# Author: Yihang Xu
+# Date: 2 November 2024
+# Contact: joker.xu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: No
+# Any other information needed? No
 
 
 #### Workspace setup ####
 library(tidyverse)
-library(rstanarm)
+library(ggplot2)
+library(dplyr)
+library(reshape2)
 
+set.seed(10086)
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+NYT_data <- read_csv("/Users/xuyihang/Desktop/2024-US-Presidential-Election-Forecast-main/data/02-analysis_data/NYT_data.csv")
 
-### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
+#### Model Data ####
+#Simple Linear Model to predict pollscore based on sample_size
+model <- lm(pollscore ~ sample_size, data = NYT_data)
+
+# Summary of the model
+summary(model)
+
+# Visualize model fit
+plot(NYT_data$sample_size, NYT_data$pollscore, main = "Sample Size vs Poll Score", xlab = "Sample Size", ylab = "Poll Score", pch = 19, col = "darkblue")
+abline(model, col = "red", lwd = 2)
 
 
 #### Save model ####
-saveRDS(
-  first_model,
-  file = "models/first_model.rds"
-)
+saveRDS(model, file = "pollscore_model.rds")
+
 
 

### 2024-11-03 paper/paper.qmd
update appendix two

@@
 
-# Appendix {-}
+# Appendix {1}
 
+# Appendix {2}
+Idealized Methodology and Survey for Forecasting the US Presidential Election
+
+1. Budget Allocation Overview
+
+With a total budget of $100K, the funds would be allocated as follows:
+
+Survey Design and Platform Costs: $5,000
+
+Respondent Recruitment (Incentives and Advertising): $60,000
+
+Sampling Management and Data Validation: $15,000
+
+Analysis and Poll Aggregation Infrastructure: $10,000
+
+Contingency and Miscellaneous Costs: $10,000
+
+2. Sampling Approach
+
+Target Population: The target population would be registered voters across the United States, ensuring representation from different demographics including age, gender, ethnicity, and political affiliation.
+
+Sampling Method:
+
+Stratified Random Sampling: To ensure proportional representation of various subgroups (e.g., regions, demographics), we will divide the population into strata and randomly select respondents from each stratum.
+
+Sample Size: The goal is to survey 10,000 respondents to maintain a balance between precision and budget constraints.
+
+Recruitment Strategy:
+
+Online Panels: Use reputable online survey panels to reach diverse respondents.
+
+Targeted Advertising: Run social media and digital ads to recruit additional respondents, particularly in underrepresented areas.
+
+Incentives: Offer monetary incentives (e.g., $5 per respondent) to increase participation.
+
+3. Data Validation
+
+To maintain data integrity, the following checks will be implemented:
+
+Response Quality Control: Implement screening questions and attention checks to ensure respondents are engaged.
+
+IP Address Monitoring: Ensure unique responses by blocking multiple submissions from the same IP address.
+
+Completion Time Analysis: Flag responses that fall outside reasonable time frames (e.g., completed too quickly).
+
+Ethical Considerations: All data will be collected anonymously, and respondents will be informed of their rights, including the right to withdraw from the survey at any time.
+Personal data will not be shared or used beyond the scope of this survey.
+
+4. Poll Aggregation and Methodology
+
+Weighting: Apply post-stratification weighting based on census data to ensure the sample aligns with the US voter demographics.
+
+Error Margin and Confidence Intervals: Report results with a calculated margin of error (typically around ±3%) and a 95% confidence interval.
+
+Aggregation of Poll Results: Collect and combine data from multiple waves of polling to smooth out any anomalies and better predict trends.
+
+Adjustments for Non-Response Bias: Implement statistical adjustments to account for known biases in survey responses.
+
+5. Implementation Platform
+
+The survey will be hosted on Google Forms to streamline data collection and integration. A direct link to the live survey is included below:
+
+Access the Survey Here: https://docs.google.com/forms/d/e/1FAIpQLSclP877Z1gT9nANFAUPrOz_K6IV6HOQXicb_cL0gwPRzhzpJw/viewform?usp=sf_link
+
+6. Survey Copy
+
+Below is a more comprehensive sample of the survey questions:
+
+Survey Title: US Presidential Election 2024: Voter Opinion and Key Issues Survey
+
+Introduction: Thank you for participating in our comprehensive survey on the upcoming US presidential election.
+Your responses are vital for understanding public sentiment and will remain confidential.
+Participation is voluntary, and you may skip any question or withdraw at any time.
+
+1. Are you a registered voter?
+
+Yes
+
+No
+
+2. Which state do you reside in?
+
+3. What is your age group?
+
+18-24
+
+25-34
+
+35-44
+
+45-54
+
+55-64
+
+65+
+
+4. Which racial or ethnic group(s) do you identify with? (Select all that apply)
+
+White/Caucasian
+
+Black/African American
+
+Hispanic/Latino
+
+Asian/Pacific Islander
+
+Native American
+
+Other (please specify)
+
+Prefer not to say
+
+5. What is your highest level of education?
+
+Less than high school
+
+High school diploma or GED
+
+Some college, no degree
+
+Associate degree (e.g., AA, AS)
+
+Bachelor’s degree (e.g., BA, BS)
+
+Master’s degree (e.g., MA, MS, MEd)
+
+Professional degree (e.g., JD, MD)
+
+Doctoral degree (e.g., PhD, EdD)
+
+Prefer not to say
+
+6. What is your gender?
+
+Male
+
+Female
+
+Non-binary/Third gender
+
+Prefer not to say
+
+7. Which candidate do you currently intend to vote for in the upcoming presidential election?
+
+Kamala Harris
+
+Donald Trump
+
+Other
+
+Undecided
+
+8. What is your political affiliation?
+
+Democrat
+
+Republican
+
+Independent
+
+Other
+
+Prefer not to say
+
+9. How confident are you in your choice for the presidential election?
+
+Very confident
+
+Somewhat confident
+
+Not very confident
+
+Not confident at all
+
+10. What is the most important issue influencing your vote? (Choose the top 3)
+
+Healthcare
+
+Economy
+
+Immigration
+
+Climate Change
+
+Education
+
+National Security
+
+Social Justice
+
+Other (please specify)
+
+11. How often do you follow news and updates about the election?
+
+Daily
+
+Weekly
+
+Occasionally
+
+Rarely
+
+Never
+
+End of Survey: Thank you for your time and valuable input. Your responses will contribute significantly to our understanding of public opinion regarding the upcoming presidential election.
 # References

### 2024-11-04 paper/paper.qmd
Update by Doran
-Delete stater files
-Update paper.qmd and paper.pdf
-Upload new clean_data

@@
 clean_data <- read_csv("../data/01-raw_data/clean_data.csv")
-raw_data <- read_csv("../data/01-raw_data/president_polls.csv")
 nyt_data <- read_csv("../data/02-analysis_data/NYT_data.csv")
+cleaned_data <- read_csv("../data/02-analysis_data/cleaned_data.csv")
+model_data <- read_csv("../data/02-analysis_data/cleaned_data.csv")
 ```
@@
 
-clean_data |>
-  select(1:5) |>      # Select the first 3 columns
+cleaned_data |>
+  select(everything()) |>      # Select the first 3 columns
   head(5) |>
   kable(
-    col.names = names(clean_data)[1:5],  # Automatically get the first 3 column names to match data
+    col.names = names(cleaned_data)[1:ncol(cleaned_data)],  # Automatically get the first 3 column names to match data
     booktabs = TRUE
   )
-```
-
-```{r}
-#| label: fig-distribution_Answers
-#| fig-cap: Distribution of Answers
-#| echo: false
-#| warning: false
-#| message: false
-
-ggplot(clean_data, aes(x = answer)) +
-  geom_bar(fill = "red", color = "black") +
-  labs(x = "Answer", y = "Count") +
-  theme_minimal()
-```
-
-```{r}
-#| label: fig-histogram_pct
-#| fig-cap: Percentage of Support for Each Candidate
-#| echo: false
-#| warning: false
-#| message: false
-
-ggplot(clean_data, aes(x = answer, y = pct, fill = party)) +
-  geom_bar(stat = "identity", color = "black") +
-  labs( x = "Candidate", y = "Percentage") +
-  theme_minimal() +
-  scale_y_continuous(labels = scales::percent_format(scale = 1)) + # Converts y-axis to percentage format
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotates x-axis labels
 ```
@@
 #| message: false
-trump_data <- raw_data %>% filter(candidate_name == "Donald Trump")
+trump_data <- cleaned_data %>% filter(answer == "Trump")
 trump_model <- lm(pct ~ pollscore + sample_size + numeric_grade + transparency_score, data = trump_data)
@@
 #| message: false
-harris_data <- raw_data %>% filter(candidate_name == "Kamala Harris")
+harris_data <- model_data %>% filter(answer == "Harris")
 harris_model <- lm(pct ~ pollscore + sample_size + numeric_grade + transparency_score, data = harris_data)
@@
 # Results
+
+```{r}
+#| label: fig-distribution_Answers
+#| fig-cap: Distribution of Answers
+#| echo: false
+#| warning: false
+#| message: false
+
+ggplot(cleaned_data %>% filter(answer %in% c("Trump", "Harris")), aes(x = answer)) +
+  geom_bar(fill = "black", color = "black") +
+  labs(x = "Answer", y = "Count") +
+  theme_minimal()
+```
+
+```{r}
+#| label: fig-histogram_pct
+#| fig-cap: Percentage of Support for Each Candidate
+#| echo: false
+#| warning: false
+#| message: false
+
+ggplot(cleaned_data %>% filter(answer %in% c("Trump", "Harris")), aes(x = answer, y = pct, fill = party)) +
+  geom_bar(stat = "identity", color = "black") +
+  labs( x = "Candidate", y = "Percentage") +
+  theme_minimal() +
+  scale_y_continuous(labels = scales::percent_format(scale = 1)) + # Converts y-axis to percentage format
+  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotates x-axis labels
+```
+
+```{r}
+#| label: fig-pct_overtime
+#| fig-cap: Mean Percentage of Support for Trump and Harris over time
+#| echo: false
+#| warning: false
+#| message: false
+#| 
+trump_data <- cleaned_data %>%
+  filter(answer == "Trump") %>%
+  mutate(end_date = mdy(end_date)) %>%  # Convert end_date to Date format
+  group_by(end_date) %>%
+  summarize(mean_pct = mean(pct, na.rm = TRUE))
+
+ggplot(trump_data, aes(x = end_date, y = mean_pct)) +
+  geom_smooth(method = "loess", color = "red", fill = "#FF7F7F", linetype = "solid", size = 1.3, se = TRUE, ) +
+  annotate("text", 
+           x = max(trump_data$end_date), 
+           y = trump_data$mean_pct[which.max(trump_data$end_date)], 
+           label = paste0("Trump ", round(trump_data$mean_pct[which.max(trump_data$end_date)], 1), "%"),
+           color = "red", 
+           fontface = "bold",
+           size = 2) +
+  labs(title = NULL, x = "Date", y = "Percentage") +
+  theme_minimal() +
+    theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank())
+
+```
+
 ## Trump
@@
 
-# Appendix {1}
+\newpage
 
-# Appendix {2}
+\appendix
+
+# Appendix {-}
+
+# Discussion of the survey’s methodology of Siena/NYT
+
+## Population, Frame, and Sample
+
+-Population:
+
+-Frame:
+
+-Sample:
+a topline sample size of at least 100
+
+## Sample Recruitment Method
+
+## Sampling Approach's trade-offs
+
+-Strengths:
+
+-Weaknesses:
+
+## How is non-response handled
+
+## What is good and bad about the questionnaire
+
+### Advantages
+
+### Disadvantages
+
+# The idealized Methodology and Survey of forecasting the US presidential election
 Idealized Methodology and Survey for Forecasting the US Presidential Election
@@
 
-1. Are you a registered voter?
+  Q1. Are you a registered voter?
 
-Yes
+ \hspace{1cm} Yes
 
-No
+ \hspace{1cm} No
 
-2. Which state do you reside in?
+  Q2. Which state do you reside in?
 
-3. What is your age group?
+  Q3. What is your age group?
 
-18-24
+  \hspace{1cm} 18-24
 
-25-34
+  \hspace{1cm} 25-34
 
-35-44
+  \hspace{1cm} 35-44
 
-45-54
+  \hspace{1cm} 45-54
 
-55-64
+  \hspace{1cm} 55-64
 
-65+
+  \hspace{1cm} 65+
 
-4. Which racial or ethnic group(s) do you identify with? (Select all that apply)
+  Q4. Which racial or ethnic group(s) do you identify with? (Select all that apply)
 
-White/Caucasian
+  \hspace{1cm}  White/Caucasian
 
-Black/African American
+  \hspace{1cm}  Black/African American
 
-Hispanic/Latino
+  \hspace{1cm}  Hispanic/Latino
 
-Asian/Pacific Islander
+  \hspace{1cm}  Asian/Pacific Islander
 
-Native American
+  \hspace{1cm}  Native American
 
-Other (please specify)
+  \hspace{1cm}  Other (please specify)
 
-Prefer not to say
+  \hspace{1cm}  Prefer not to say
 
-5. What is your highest level of education?
+  Q5. What is your highest level of education?
 
-Less than high school
+  \hspace{1cm}  Less than high school
 
-High school diploma or GED
+  \hspace{1cm}  High school diploma or GED
 
-Some college, no degree
+  \hspace{1cm}  Some college, no degree
 
-Associate degree (e.g., AA, AS)
+  \hspace{1cm}  Associate degree (e.g., AA, AS)
 
-Bachelor’s degree (e.g., BA, BS)
+  \hspace{1cm}  Bachelor’s degree (e.g., BA, BS)
 
-Master’s degree (e.g., MA, MS, MEd)
+  \hspace{1cm}  Master’s degree (e.g., MA, MS, MEd)
 
-Professional degree (e.g., JD, MD)
+  \hspace{1cm}  Professional degree (e.g., JD, MD)
 
-Doctoral degree (e.g., PhD, EdD)
+  \hspace{1cm}  Doctoral degree (e.g., PhD, EdD)
 
-Prefer not to say
+  \hspace{1cm}  Prefer not to say
 
-6. What is your gender?
+  Q6. What is your gender?
 
@@
 
-7. Which candidate do you currently intend to vote for in the upcoming presidential election?
+ Q7. Which candidate do you currently intend to vote for in the upcoming presidential election?
 
@@
 
-8. What is your political affiliation?
+  Q8. What is your political affiliation?
 
@@
 
-9. How confident are you in your choice for the presidential election?
+  Q9. How confident are you in your choice for the presidential election?
 
@@
 
-10. What is the most important issue influencing your vote? (Choose the top 3)
+  Q10. What is the most important issue influencing your vote? (Choose the top 3)
 
@@
 
-11. How often do you follow news and updates about the election?
+  Q11. How often do you follow news and updates about the election?
 
@@
 End of Survey: Thank you for your time and valuable input. Your responses will contribute significantly to our understanding of public opinion regarding the upcoming presidential election.
+
+\newpage
+
 # References

### 2024-11-04 scripts/03-clean_data.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Cleans the president polls data to the Siena/NYT pollster only data [...UPDATE THIS...]
+# Purpose: Cleans the president polls data
 # Author: 
 # Date:
 # Contact: 
@@ -8,10 +8,18 @@
 
 #### Workspace setup ####
 library(tidyverse)
-
-#### Clean data ####
+library(janitor)
+library(tidyr)
 raw_data <- read_csv("data/01-raw_data/president_polls.csv")
 
+#### Clean data ####
+cleaned_data <-
+  raw_data |>
+  janitor::clean_names() |>
+  select(answer, pct, pollster, methodology, population, population_full, sample_size, numeric_grade, pollscore, party,transparency_score) |>
+  tidyr::drop_na()
+  
+#### Clean data with "NYT" pollster only ####
 NYT_data <-
   raw_data |>
   janitor::clean_names() |>
@@ -19,6 +27,12 @@ NYT_data <-
   filter(pollster == "Siena/NYT") |>
   tidyr::drop_na()
 
+#### Model data ####
+model_data <-
+  clean_data |>
+  select(answer,pct,sample_size,numeric_grade,transparency_score,pollscore)
+
 #### Save data ####
 write_csv(NYT_data, "data/02-analysis_data/NYT_data.csv")
-
+write_csv(cleaned_data, "data/02-analysis_data/cleaned_data.csv")
+write_csv(model_data, "data/02-analysis_data/model_data.csv")

### 2024-11-04 paper/paper.qmd
Update by Doran
-Update paper.qmd, paper.pdf, and references.bib
-Update the new clean_data with no NA value

@@
 
-## Sample Data
+## Sample Clean Data
 
@@
 cleaned_data |>
-  select(everything()) |>      # Select the first 3 columns
+  select(answer,pct,pollster,methodology,sample_size) |>      # Select the first 3 columns
   head(5) |>
   kable(
-    col.names = names(cleaned_data)[1:ncol(cleaned_data)],  # Automatically get the first 3 column names to match data
+    col.names = c("Answer","Percentage","Pollster","Methodology","Sample Size"),  # Automatically get the first 3 column names to match data
     booktabs = TRUE
@@
 ```
+
+The @tbl-cleaned_data shows the 5 of all colunms.
 
@@
 
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-nyt_data
+#| tbl-cap: "Sample Siena/NYT Data"
+#| warning: false
+
+nyt_data |>
+  select(everything()) |>
+  head(5) |>
+  kable(
+    col.names = c("Pollster","Methodology","Population","Sample Size","Grade Rating","Pollscore"),
+    booktabs = TRUE
+  )
+```
+
+## Background and Intro
+The New York Times/Siena College Poll is a collaborative effort between The New York Times and the Siena College Research Institute, renowned for its methodological rigor and accuracy.
+The @tbl-nyt_data above shows sample data of Seina/NYT from clean data, which contains some useful information.
+According to FiveThirtyEight's pollster ratings, this partnership holds a 3.0-star rating as shown @tbl-nyt_data, indicating high reliability.
+Based on the section Methodological standards from FAQS of FiveThirtyEight[@fivethirtyeightFAQ], "Pollsters must also be able to answer basic questions about their methodology, including but not limited to the polling mode used (e.g., telephone calls, text messages, online panels), the source of their sample, their weighting criteria and the source of the poll's funding.
+In most cases, a detailed written methodology statement is sufficient to satisfy this criterion, but we may contact pollsters directly to clarify methodological details and follow up occasionally to ensure the pollster is still meeting our standards." Their data will ensure that pollsters maintain methodological standards.
+More specific details about NYT/SEINA's methodology are discussed below.
+
 ## Population, Frame, and Sample
+ - Population:
+The target population comprises likely voters in the United States, focusing on those eligible and expected to participate in the upcoming election.
 
--Population:
+ - Frame:
+The sampling frame is constructed from voter registration lists, which are comprehensive databases of registered voters across various states.
 
--Frame:
-
--Sample:
-a topline sample size of at least 100
+ - Sample:
+A stratified random sample is drawn from the voter registration lists, ensuring representation across key demographics such as age, gender, race, education, and geographic location.A topline sample size of at least 100 [@fivethirtyeightFAQ].
 
 ## Sample Recruitment Method
+Participants are recruited through a combination of landline and mobile phone calls(like the Methodology in @tbl-nyt_data).
+This dual approach addresses the decline in landline usage and aims to reach a broader demographic spectrum.
+The use of voter registration lists enhances the likelihood of contacting registered voters, thereby improving the sample's representativeness.
 
@@
 
--Strengths:
+### Advantages
+Enhances representativeness by ensuring all key subgroups are included.
+Improves precision in estimates for specific subpopulations.
 
--Weaknesses:
+### Disadvantages
+More complex and time-consuming compared to simple random sampling.
+Requires accurate and up-to-date information on the stratification variables.
+Handling Non-Response:
 
 ## How is non-response handled
+Non-response is addressed through weighting adjustments.
+Post-stratification weights are applied to align the sample with known population parameters, such as age, gender, race, and education.
+This process mitigates biases arising from differential response rates among various demographic groups.
 
@@
 ### Advantages
+ - Questions are crafted to be clear and unbiased, minimizing misinterpretation.
+The questionnaire covers a broad range of topics, providing comprehensive insights into voter opinions.
 
 ### Disadvantages
+ - The length of the questionnaire may lead to respondent fatigue, potentially affecting the quality of responses
+ - The mode of administration (telephone interviews) might introduce social desirability bias, where respondents provide answers they perceive as socially acceptable rather than their true beliefs.
+
+## Summary
+Overall, the New York Times/Siena College Poll employs robust methodologies to ensure accurate and reliable insights into voter preferences and behaviors.
 
@@
 
-Access the Survey Here: https://docs.google.com/forms/d/e/1FAIpQLSclP877Z1gT9nANFAUPrOz_K6IV6HOQXicb_cL0gwPRzhzpJw/viewform?usp=sf_link
+Access the Survey Here: [US Presidential Election 2024: Voter Opinion and Key Issues Survey](https://docs.google.com/forms/d/e/1FAIpQLSclP877Z1gT9nANFAUPrOz_K6IV6HOQXicb_cL0gwPRzhzpJw/viewform?usp=sf_link)
 
@@
 
-    Male
+  \hspace{1cm}  Male
 
-    Female
+  \hspace{1cm}  Female
 
-    Non-binary/Third gender
+  \hspace{1cm}  Non-binary/Third gender
 
-    Prefer not to say
+  \hspace{1cm}  Prefer not to say
 
@@
 
-    Kamala Harris
+  \hspace{1cm} Kamala Harris
 
-    Donald Trump
+  \hspace{1cm}  Donald Trump
 
-    Other
+  \hspace{1cm} Other
 
-    Undecided
+  \hspace{1cm}  Undecided
 
@@
 
-    Democrat
+  \hspace{1cm} Democrat
 
-    Republican
+  \hspace{1cm} Republican
 
-    Independent
+  \hspace{1cm}  Independent
 
-    Other
+  \hspace{1cm}  Other
 
-    Prefer not to say
+  \hspace{1cm}  Prefer not to say
 
@@
 
-    Very confident
+  \hspace{1cm}  Very confident
 
-    Somewhat confident
+  \hspace{1cm}  Somewhat confident
 
-    Not very confident
+  \hspace{1cm}  Not very confident
 
@@
 
-    Healthcare
+  \hspace{1cm}  Healthcare
 
-    Economy
+  \hspace{1cm}  Economy
 
-    Immigration
+  \hspace{1cm}    Immigration
 
-    Climate Change
+  \hspace{1cm}  Climate Change
 
-    Education
+  \hspace{1cm}  Education
 
-    National Security
+  \hspace{1cm}  National Security
 
-    Social Justice
+  \hspace{1cm}  Social Justice
 
-    Other (please specify)
+  \hspace{1cm}  Other (please specify)
 
@@
 
-    Daily
+  \hspace{1cm}  Daily
 
-    Weekly
+  \hspace{1cm}  Weekly
 
-    Occasionally
+  \hspace{1cm}  Occasionally
 
-    Rarely
+  \hspace{1cm}  Rarely
 
-    Never
+  \hspace{1cm}  Never
 

### 2024-11-04 scripts/02-download_data.R

@@ -23,5 +23,6 @@ clean_data <- raw_data |> select(pollster, display_name,
                                  party, answer, candidate_name, pct) %>%
   filter(pollster=="Siena/NYT") %>% filter(!is.na(state))
 
+
 #### Save data ####
 write_csv(clean_data, "data/01-raw_data/clean_data.csv")

### 2024-11-04 scripts/03-clean_data.R

@@ -16,14 +16,15 @@ raw_data <- read_csv("data/01-raw_data/president_polls.csv")
 cleaned_data <-
   raw_data |>
   janitor::clean_names() |>
-  select(answer, pct, pollster, methodology, population, population_full, sample_size, numeric_grade, pollscore, party,transparency_score) |>
+  select(answer, pct, pollster, methodology, population, sample_size, 
+         numeric_grade, pollscore, party,transparency_score,end_date) |>
   tidyr::drop_na()
   
 #### Clean data with "NYT" pollster only ####
 NYT_data <-
-  raw_data |>
+  cleaned_data |>
   janitor::clean_names() |>
-  select(pollster,methodology,population,population_full,sample_size,numeric_grade,pollscore) |>
+  select(pollster,methodology,population,sample_size,numeric_grade,pollscore) |>
   filter(pollster == "Siena/NYT") |>
   tidyr::drop_na()
 

### 2024-11-04 scripts/00-simulate_data.R
Update by Doran

@@ -1,12 +1,12 @@
 #### Preamble ####
-# Purpose: Simulates a dataset of Australian electoral divisions, including the 
-  #state and party that won each division.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Simulates a dataset of Presidential Election Polls
+# Author: Doran Wang
+# Date: 21 October 2024
+# Contact: doran.wang@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: The `tidyverse` package must be installed
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Any other information needed? Make sure you are in the 
+  #`2024_US_Presidential_Election_Forecast` rproj
 
 
 #### Workspace setup ####

### 2024-11-04 scripts/01-test_simulated_data.R

@@ -1,14 +1,15 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated Australian 
-  #electoral divisions dataset.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Tests the structure and validity of the simulated Presidential
+  #Election Polls dataset.
+# Author: Doran Wang
+# Date: 21 October 2024
+# Contact: doran.wang@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
   # - The `tidyverse` package must be installed and loaded
   # - 00-simulate_data.R must have been run
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Any other information needed? Make sure you are in the
+  #`2024_US_Presidential_Election_Forecast` rproj
 
 
 #### Workspace setup ####

### 2024-11-04 scripts/03-clean_data.R

@@ -1,10 +1,13 @@
 #### Preamble ####
 # Purpose: Cleans the president polls data
-# Author: 
-# Date:
-# Contact: 
+# Author: Doran Wang
+# Date: 21 October 2024
+# Contact: doran.wang@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: Access to the president_polls.csv first
+# Any other information needed? Make sure you are in the 
+  #`2024_US_Presidential_Election_Forecast` rproj
+
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-11-04 paper/paper.qmd
update paper.qmd

@@
 ```
+## Measurement
+In the data section, a thorough discussion of measurement is essential to clarify how real-world phenomena are represented as entries within the dataset.
+For this dataset, the primary variables, including pct (percentage support), poll score, sample size, numeric grade, and transparency score, all serve as quantifiable indicators of complex social and political sentiments or behaviors.
+
+Each entry in the dataset captures a snapshot of voter sentiment for a candidate within a specific poll.
+The pct variable measures the proportion of poll respondents who support a candidate, translating public approval into a concrete percentage that reflects their popularity.
+This measurement begins with a real-world event (a poll survey), where respondents answer questions indicating their voting intentions.
+These responses are aggregated to create a support percentage, pct, which becomes an entry in the dataset.
+
+Similarly, poll score reflects an additional standardized metric of support and is often calculated by polling agencies using a combination of raw support data and weighting based on demographic or political factors.
+The sample size variable records the number of respondents in each poll, giving context to the robustness of each poll’s data.
+Larger sample sizes indicate a broader cross-section of public opinion, lending greater credibility to the findings, while smaller samples may reflect more niche or variable groups.
+
+For numeric grade, experts or rating agencies assign a score based on the candidate's perceived qualifications and performance, creating a quantifiable indicator that reflects subjective evaluations.
+These evaluations are derived from real-world assessments of a candidate’s leadership, expertise, and public image.
+Transparency score measures the perceived openness of a candidate’s communication, where third-party assessments, or even voter ratings, can be collected and standardized into a numeric value representing public trust or perceived honesty.
+
+Through these variables, real-world opinions, demographic factors, and subjective assessments are transformed into measurable data points that allow for analysis and comparison.
+Each entry represents a combination of individual-level opinions and expert evaluations, providing a structured view of candidate support across diverse groups and contexts.
+This approach ensures that complex social and political phenomena are systematically captured and made accessible for further investigation.
+
+## Response variable
+
+The response variable, pct, represents the percentage of positive support or approval for each candidate within a given poll or data sample.
+It quantifies the portion of respondents expressing favorable views or intentions to vote for the candidate.
+This variable is essential in assessing the candidates’ overall popularity and provides a measurable outcome that can be influenced by several predictors, such as poll score, sample size, numeric grade, and transparency score.
+A higher pct value indicates stronger support, while lower values suggest less favorable voter sentiment.
+Understanding the predictors’ impact on pct can offer valuable insights into factors driving public opinion and help to project likely election outcomes.
+
+```{r}
+#| label: Distribution of Percentage
+#| echo: false
+#| warning: false
+#| message: false
+ggplot(cleaned_data, aes(x = pct)) +
+  geom_histogram(binwidth = 5, fill = "skyblue", color = "black") +
+  labs(title = "Distribution of Percentage", x = "Percentage (%)", y = "Frequency") +
+  theme_minimal()
+```
+
+## Predictors variable
+The transparency score is a predictor variable that reflects the level of openness, honesty, and accessibility perceived in a candidate’s campaign or governance approach.
+This score typically evaluates factors like the availability of public records, clarity in policy positions, accountability to voters, and the perceived integrity of the candidate.
+Higher transparency scores generally suggest a campaign or candidate who is more forthcoming with information and responsive to public scrutiny, which can enhance public trust.
+However, transparency does not always translate to higher support; it may appeal to certain voter demographics while alienating others who prioritize different traits, such as assertiveness or policy efficiency.
+In the models for both Trump and Harris, transparency score showed different effects, indicating it might play a nuanced role in influencing overall voter support and trust in each candidate’s leadership style.
+```{r}
+#| label: fig-distribution_transparency_score
+#| echo: false
+#| warning: false
+#| message: false
+ggplot(cleaned_data, aes(x = transparency_score)) +
+  geom_histogram(binwidth = 2, fill = "skyblue", color = "black") +
+  labs(title = "Distribution of transparency score", x = "transparency score", y = "Frequency") +
+  theme_minimal()
+```
+
+Sample size and poll score are key predictor variables that help gauge the reliability and context of each poll’s findings.
+Sample size represents the number of respondents participating in the poll, with larger sample sizes generally providing more reliable estimates of the population's opinion due to a lower margin of error.
+When sample size is small, the results may be more volatile and less reflective of the general public.
+Meanwhile, poll score is an indicator of each candidate's popularity or approval rating within the specific poll, often presented as a numeric score that reflects the overall support level among respondents.
+A higher poll score indicates stronger support, while a lower score suggests less favorable sentiment.
+Together, sample size and poll score give insight into the strength and representativeness of the candidate's support in each dataset; they reveal how solid and widespread the approval may be, influencing interpretations of the candidate’s standing and potential for success in a larger electoral context.
+
+```{r}
+#| label: Poll Score by Sample Size and Transparency Score
+#| echo: false
+#| warning: false
+#| message: false
+ggplot(cleaned_data, aes(x = sample_size, y = pollscore)) +
+  geom_point(aes(color = transparency_score)) +
+  facet_wrap(~ numeric_grade) +
+  labs(title = "Poll Score by Sample Size and Transparency Score", x = "Sample Size", y = "Poll Score", color = "Transparency Score") +
+  theme_minimal()
+```
+
+The numeric grade is a predictor variable that quantifies a candidate's perceived quality or effectiveness, often assigned by analysts or rating agencies based on various performance criteria.
+This score can encompass factors such as policy effectiveness, leadership skills, public speaking, and issue-specific expertise.
+A higher numeric grade suggests that the candidate is viewed favorably across these performance metrics, signaling a strong competency level.
+This metric can heavily influence voter support, as it provides a consolidated assessment of the candidate’s qualifications and perceived ability to fulfill public expectations.
+In the models for Trump and Harris, the numeric grade had differing impacts on the outcome variable, with a positive relationship in Harris's model and a negative one in Trump's.
+These contrasts suggest that voters' interpretations of "quality" or "effectiveness" may vary significantly between the candidates, affecting each one's appeal in distinct ways.
+
+```{r}
+#| label: Poll Score by Numeric Grade
+#| echo: false
+#| warning: false
+#| message: false
+ggplot(cleaned_data, aes(x = factor(numeric_grade), y = pollscore)) +
+  geom_boxplot(fill = "lightgreen") +
+  labs(title = "Poll Score by Numeric Grade", x = "Numeric Grade", y = "Poll Score") +
+  theme_minimal()
+
+```
 
@@
 ggplot(cleaned_data %>% filter(answer %in% c("Trump", "Harris")), aes(x = answer)) +
-  geom_bar(fill = "black", color = "black") +
+  geom_bar(fill = "pink", color = "pink") +
   labs(x = "Answer", y = "Count") +
@@
 ggplot(cleaned_data %>% filter(answer %in% c("Trump", "Harris")), aes(x = answer, y = pct, fill = party)) +
-  geom_bar(stat = "identity", color = "black") +
+  geom_bar(stat = "identity", color = "lightblue") +
   labs( x = "Candidate", y = "Percentage") +
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotates x-axis labels
+```
+
+```{r}
+#| label: transparency score for each candidate
+#| fig-cap: Percentage of Support for Each Candidate
+#| echo: false
+#| warning: false
+#| message: false
+ggplot(cleaned_data, aes(x = answer, y = transparency_score, fill = answer)) +
+  geom_boxplot() +
+  labs(title = "Transparency Score by Candidate", x = "Candidate", y = "Transparency Score") +
+  theme_minimal() +
+  theme(legend.position = "none")
 ```

### 2024-11-04 paper/paper.qmd
update paper.qmd

@@
 ```{r}
-#| label: Distribution of Percentage
+#| label: fig-percentage
+#| fig-cap: Distribution of Percentage
 #| echo: false
@@
   geom_histogram(binwidth = 5, fill = "skyblue", color = "black") +
-  labs(title = "Distribution of Percentage", x = "Percentage (%)", y = "Frequency") +
+  labs(x = "Percentage (%)", y = "Frequency") +
   theme_minimal()
@@
 In the models for both Trump and Harris, transparency score showed different effects, indicating it might play a nuanced role in influencing overall voter support and trust in each candidate’s leadership style.
+
 ```{r}
 #| label: fig-distribution_transparency_score
+#| fig-cap: Distribution of transparency score
 #| echo: false
@@
   geom_histogram(binwidth = 2, fill = "skyblue", color = "black") +
-  labs(title = "Distribution of transparency score", x = "transparency score", y = "Frequency") +
+  labs(x = "transparency score", y = "Frequency") +
   theme_minimal()
@@
 ```{r}
-#| label: Poll Score by Sample Size and Transparency Score
+#| label: fig-poll_score
+#| fig-cap: Poll Score by Sample Size and Transparency Score
 #| echo: false
@@
   facet_wrap(~ numeric_grade) +
-  labs(title = "Poll Score by Sample Size and Transparency Score", x = "Sample Size", y = "Poll Score", color = "Transparency Score") +
+  labs(x = "Sample Size", y = "Poll Score", color = "Transparency Score") +
   theme_minimal()

### 2024-11-04 paper/paper.qmd
Update by Doran
-Change the type of csv to parquet
-Change the clean_data.R

--- 2024-11-04 paper/paper.qmd
@@
 library(knitr)
+library(arrow)
 
-clean_data <- read_csv("../data/01-raw_data/clean_data.csv")
-nyt_data <- read_csv("../data/02-analysis_data/NYT_data.csv")
-cleaned_data <- read_csv("../data/02-analysis_data/cleaned_data.csv")
-model_data <- read_csv("../data/02-analysis_data/cleaned_data.csv")
+nyt_data <- read_parquet("../data/02-analysis_data/NYT_data.parquet")
+cleaned_data <- read_parquet("../data/02-analysis_data/cleaned_data.parquet")
+model_data <- read_parquet("../data/02-analysis_data/cleaned_data.parquet")
 ```

### 2024-11-04 scripts/03-clean_data.R

@@ -13,6 +13,7 @@
 library(tidyverse)
 library(janitor)
 library(tidyr)
+library(arrow)
 raw_data <- read_csv("data/01-raw_data/president_polls.csv")
 
 #### Clean data ####
@@ -33,10 +34,10 @@ NYT_data <-
 
 #### Model data ####
 model_data <-
-  clean_data |>
+  cleaned_data |>
   select(answer,pct,sample_size,numeric_grade,transparency_score,pollscore)
 
 #### Save data ####
-write_csv(NYT_data, "data/02-analysis_data/NYT_data.csv")
-write_csv(cleaned_data, "data/02-analysis_data/cleaned_data.csv")
-write_csv(model_data, "data/02-analysis_data/model_data.csv")
+write_parquet(NYT_data, "data/02-analysis_data/NYT_data.parquet")  # Save as Parquet
+write_parquet(cleaned_data, "data/02-analysis_data/cleaned_data.parquet")  # Save as Parquet
+write_parquet(model_data, "data/02-analysis_data/model_data.parquet")

### 2024-11-04 paper/paper.qmd
update paper.qmd

--- 2024-11-04 paper/paper.qmd
@@
 title: "2024 US Presidential Election Forecast Model"
-subtitle: "My subtitle if needed"
 author: 
@@
 Data were cleaned and analyzed using the open source statistical programming language R [@citeR].
-Libraries `tidyverse` [@citeTidyverse], `janitor` [@Citejan], `knitr` [@citeknitr], and `dplyr` [@citedplyr] were used for simulating, cleaning and testing.
+Libraries `tidyverse` [@citeTidyverse], `arrow` [@citearrow] `janitor` [@Citejan], `knitr` [@citeknitr], and `dplyr` [@citedplyr] were used for simulating, cleaning and testing.
 Graphics were made using `ggplot2` [@citeGG].
@@
 
-The @tbl-cleaned_data shows the 5 of all colunms.
-
 # Model
@@
 #| fig-cap: Distribution of Answers
+#| fig-width: 2
+#| fig-height: 2
 #| echo: false
@@
 ```
+```{r}
+#| label: fig-pollster_party
+#| fig-cap: Count of Polls by Pollster and Party
+#| fig-width: 2
+#| fig-height: 2
+#| echo: false
+#| warning: false
+#| message: false
+filter_data <- cleaned_data %>%
+  filter(answer %in% c("Trump", "Harris"))
 
+ggplot(filter_data, aes(x = answer, y = pct)) +
+  geom_point(color = "steelblue", alpha = 0.6) +  # Points with some transparency
+  labs(title = "Relationship between Answer and Percentage", 
+       x = "Answer", 
+       y = "Percentage (pct)") +  # Labels for axes and title
+  theme_minimal()
+```
+
+## Trump
 ```{r}
-#| label: fig-histogram_pct
-#| fig-cap: Percentage of Support for Each Candidate
+#| label: fig-pct_overtime
+#| fig-cap: Mean Percentage of Support for Trump over time
+#| fig-width: 8
+#| fig-height: 3
 #| echo: false
@@
 
-ggplot(cleaned_data %>% filter(answer %in% c("Trump", "Harris")), aes(x = answer, y = pct, fill = party)) +
-  geom_bar(stat = "identity", color = "lightblue") +
-  labs( x = "Candidate", y = "Percentage") +
-  theme_minimal() +
-  scale_y_continuous(labels = scales::percent_format(scale = 1)) + # Converts y-axis to percentage format
-  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotates x-axis labels
-```
-
-```{r}
-#| label: transparency score for each candidate
-#| fig-cap: Percentage of Support for Each Candidate
-#| echo: false
-#| warning: false
-#| message: false
-ggplot(cleaned_data, aes(x = answer, y = transparency_score, fill = answer)) +
-  geom_boxplot() +
-  labs(title = "Transparency Score by Candidate", x = "Candidate", y = "Transparency Score") +
-  theme_minimal() +
-  theme(legend.position = "none")
-```
-
-```{r}
-#| label: fig-pct_overtime
-#| fig-cap: Mean Percentage of Support for Trump and Harris over time
-#| echo: false
-#| warning: false
-#| message: false
-#| 
 trump_data <- cleaned_data %>%
@@
         panel.grid.minor = element_blank())
-
 ```
-
-## Trump
 The model estimates the influence of several predictors on the dependent variable.
@@
 ## Harris
+```{r}
+#| label: fig-pct_overtime2
+#| fig-cap: Mean Percentage of Support for Harris over time
+#| fig-width: 8
+#| fig-height: 3
+#| echo: false
+#| warning: false
+#| message: false
+harris_data <- cleaned_data %>%
+  filter(answer == "Harris") %>%
+  mutate(end_date = mdy(end_date)) %>%  # Convert end_date to Date format
+  group_by(end_date) %>%
+  summarize(mean_pct = mean(pct, na.rm = TRUE))
+
+ggplot(harris_data, aes(x = end_date, y = mean_pct)) +
+  geom_smooth(method = "loess", color = "blue", fill = "blue", linetype = "solid", size = 1.3, se = TRUE, ) +
+  annotate("text", 
+           x = max(harris_data$end_date), 
+           y = harris_data$mean_pct[which.max(harris_data$end_date)], 
+           label = paste0("Harris ", round(harris_data$mean_pct[which.max(harris_data$end_date)], 1), "%"),
+           color = "blue", 
+           fontface = "bold",
+           size = 2) +
+  labs(title = NULL, x = "Date", y = "Percentage") +
+  theme_minimal() +
+    theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank())
+```
 The model investigates the impact of several predictors on the dependent variable, with the following key findings:

### 2024-11-04 scripts/06-model_data.R
update file

@@ -1,37 +1,51 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Models
+# Author: Yihang Xu
+# Date: 3 November 2024
+# Contact: joker.xu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: No
+# Any other information needed? No
 
 
 #### Workspace setup ####
 library(tidyverse)
-library(rstanarm)
+library(readr)
+library(dplyr)
+library(knitr)
+library(arrow)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+nyt_data <- read_parquet("/Users/xuyihang/Desktop/1314520hh/2024-US-Presidential-Election-Forecast/data/02-analysis_data/NYT_data.parquet")
+cleaned_data <- read_parquet("/Users/xuyihang/Desktop/1314520hh/2024-US-Presidential-Election-Forecast/data/02-analysis_data/cleaned_data.parquet")
+model_data <- read_parquet("/Users/xuyihang/Desktop/1314520hh/2024-US-Presidential-Election-Forecast/data/02-analysis_data/model_data.parquet")
 
 ### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
+trump_data <- cleaned_data %>% filter(answer == "Trump")
+trump_model <- lm(pct ~ pollscore + sample_size + numeric_grade + transparency_score, data = trump_data)
+summary(trump_model)
 
+harris_data <- model_data %>% filter(answer == "Harris")
+harris_model <- lm(pct ~ pollscore + sample_size + numeric_grade + transparency_score, data = harris_data)
+summary(harris_model)
 
 #### Save model ####
[…]

### 2024-11-04 scripts/05-exploratory_data_analysis.R
add models

@@ -16,7 +16,7 @@ library(reshape2)
 
 set.seed(10086)
 #### Read data ####
-NYT_data <- read_csv("/Users/xuyihang/Desktop/2024-US-Presidential-Election-Forecast-main/data/02-analysis_data/NYT_data.csv")
+NYT_data <- read_csv("data/02-analysis_data/NYT_data.csv")
 
 #### Model Data ####
 #Simple Linear Model to predict pollscore based on sample_size
